%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.5, 1 December 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}
\PassOptionsToPackage{lowtilde}{url}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e, normalphoto]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=0.7cm,right=9.3cm,marginparwidth=7.7cm,marginparsep=1cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

\usepackage[dvipsnames]{xcolor}
\usepackage[none]{hyphenat}

% Change the colours if you want to
\definecolor{IFBlue}{HTML}{0F6688}
\definecolor{IFDarkBlue}{HTML}{00425C}
\definecolor{IFMediumBlue}{HTML}{17739A}
\definecolor{IFLightBlue}{HTML}{228FBD}

\definecolor{IFGrey}{HTML}{6D6E71}
\definecolor{IFDarkGrey}{HTML}{231F20}
\definecolor{IFMediumGrey}{HTML}{4D4D4F}
\definecolor{IFLightGrey}{HTML}{808285}
\definecolor{bodyColor}{gray}{0.45}

\colorlet{heading}{IFBlue}
\colorlet{accent}{IFLightBlue}
\colorlet{emphasis}{IFMediumGrey}
\colorlet{body}{bodyColor}

\definecolor{dark}{gray}{0.0}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Harshit Raghuvanshi}
\tagline{Software Development Engineer}
%\photo{2.8cm}{logo}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{\href{mailto:rharshit98@gmail.com}{rharshit98@gmail.com}}
  \phone{\href{tel:+919969817450}{+91 9969817450}}
  % \location{India}
  \linkedin{\href{https://www.linkedin.com/in/Harshit-Raghuvanshi}{/in/Harshit-Raghuvanshi}}
  \github{\href{https://github.com/rharshit}{/rharshit}}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
  % \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\smallskip
Senior Software Engineer with over four years of experience at Cisco, specializing in architecting and scaling high-throughput microservices in Java and Spring Boot. Proven expertise in reducing system latency by up to 80\% and designing secure, resilient backend platforms for business-critical financial applications.\newline
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Work Experience}

\eventheader{Cisco Systems (India) Pvt. Ltd.}

\eventsubheader{SDE II \& Partner Security Architect}{November 2021 - November 2024}
% \eventdateplace{November 2021 - November 2024}{Bangalore, Karnataka, India}
\begin{itemize}
  \item Led the end-to-end development for the Rebate Engine tool as the subject matter expert, owning the complete project lifecycle.
  \item Served as a \imp{founding engineer} on the NextGen Rebate Engine platform.
  \item Led a \imp{security} overhaul across a 9 applications, eliminating 100\% of P0/P1 vulnerabilities and achieving a 90\% vulnerability reduction.
  \item Developed a \imp{multi-threaded} workflow to reduce login time by \imp{80\%}.
  \item Designed and scaled the rebate calculation service by deploying \imp{load-sharing} servers, significantly improving system throughput.
  \item Co-designed the NextGen Rebate Engine architecture, defining data models, service boundaries, and API contracts.
  \item Built a \imp{React} app to serve as UI to the NextGen Platform.
  \item Designed and implemented dynamic \imp{Lucene} queries to create and read indexes faster and speed up rebate re-calculations by upto \imp{60\%}.
\end{itemize}
\eventsubheader{SDE I}{August 2020 - October 2021}
% \eventdateplace{August 2020 - October 2021}{Bangalore, Karnataka, India}
\begin{itemize}
%  \item Created \imp{RESTful Service} as a \imp{microservice} based on \imp{Spring boot}.
%  \item Implemented \imp{OAuth 2.0} and \imp{user access management}.
%  \item Implementing \imp{database pool managers} and caching to improve performance.
%  \item Developed the complete \imp{audit log framework}.
%  \item Managed \imp{CI/CD pipelines} along with load balancer configurations.
	\item Developed and maintained a core \imp{Spring Boot} application, delivering robust \imp{RESTful APIs} for key business functionalities.
	\item Architected and delivered a reusable, platform-wide audit-log framework in Java, establishing a standardized auditing solution.
	\item Owned the implementation of primary business logic for the application, translating complex requirements into functional code.
	\item Integrated \imp{OAuth 2.0} flow, \imp{access management}, databse pool-manager, \imp{error handling}, actuators, and \imp{Swagger} into the application platform.
	\item Created and managed \imp{CI/CD} pipelines using \imp{Jenkins}.
 \end{itemize}

\eventsubheader{SDE - Intern}{January 2020 - June 2020}
% \eventdateplace{January 2020 - June 2020}{Bangalore, Karnataka, India}
\begin{itemize}
  \item Developed a POC application by merging frameworks like \imp{Struts}, \imp{Spring} and \imp{AngularJS}, optimizing and refactoring the legacy code.
  \item Built custom cache management and logging framework.
 \end{itemize}
\vspace{4pt}
\eventheader{Janitri Innovations Pvt. Ltd.}
\eventsubheader{Software Engineer and Image Processing Intern}{May 2019 - July 2019}
% \eventdateplace{May 2019 - July 2019}{Bangalore, Karnataka, India}
\begin{itemize}
  \item Built a custom image processing algorithm using \imp{OpenCV} to clean the images and process them in batches for optimal throughput.
  \item Developed \imp{Android app} using \imp{MVVM architecture} for the end user.
  \item Added \imp{multi-threading} to increase the throughput by upto 8x.
 \end{itemize}
 
 
\cvsection{Education}
\eventheader{Manipal Institute of Technology}
\eventsubheader{B.Tech in Computer and Communication Engineering}{7.84 CGPA}
\eventdateplace{August 2016 - August 2020}{Manipal, Karnataka, India}
\begin{itemize}
  \item \imp{Courses:} Object Oriented Programming, Data Structures, TCP/IP, OS, Database, Software Design, Parallel Programming, Data Mining%, Embedded Systems
\end{itemize}

\cvsection{Other positions of Responsibility}
\eventsubheader{IECSE and TechTatva}{\eventdateplace{2016-2019}{Manipal}}
\begin{itemize}
    \item Vice-Chairperson for \href{https://iecsemanipal.com/}{IECSE}, the university's largest technical club, where I mentored committees and organized developer workshops.
    \item Led multiple technical events during the TechTatva college festival.
\end{itemize}

\inv{Tags: Java, Python, C++, React, TypeScript, JavaScript, SQL, Oracle, MySql, Postgresql, Postgres, NoSQL, Mongo, MongoDb, Sharding, Bash, Script, Scripting, Docker, React, Angular, Node, Android, Kotlin, Maven, Node, Git, OpenCV, Gradle, Jenkins, Spinnaker, Kubernetes, SSH, System design, HLD, LLD, Microservices, Micro-services, Monolith, Distributed Systems, MVC, MVP, MVVM, Cache, Caching, Backend, Developer, Spring, Springboot, Spring boot, Struts, Web, Pipeline, Optimize, Optimization, DevOps, SecOps, Security, Vulnerabilities, Scava, Bava, Dava, Checkmarx, Rapid7, Lucene, Solr, Search, Kafka, Zookeeper, RabbitMQ, Messaging queues}
\end{document}
