\cvsection{Skills}
\imp{Languages:} Java, Python, TypeScript, SQL, C++\newline
\imp{Frameworks \& Libraries:} Spring Boot, React, Angular, Node.js, OpenCV, Android Framework\newline
\imp{Tools \& Technologies:} Git, Gerrit, Jenkins, Spinnaker, Maven, Docker, MongoDB\newline


\cvsection{Projects}
\eventsubheader{\href{https://github.com/rharshit/ticker_public}{Ticker}}{Automating trading algorithms}
\eventdateplace{Apr 2021 - Current}{}
\begin{itemize}
  \item Built \imp{event-driven} suite of \imp{microservices} to fetch, store, and process algorithms on real-time \imp{stock market} data.
  \item Optimized for low latency and high throughput.
  \item Inter-service communication using \imp{RESTful API}.
  \item Designed relational database schema in \imp{MySQL} and utilized \imp{Spring Data JPA} for efficient and secure data persistence and retrieval.
  \item Microservices built with \imp{Spring boot}.
  \item Designed and implemented \imp{task executors} to manage processing threads.
 \end{itemize}

 \eventsubheader{\href{https://github.com/rharshit/carwale}{CarSync}}{\eventdateplace{Jan 2025 - Feb 2025}{}}
\begin{itemize}
    \item Developed a data aggregation service using \imp{Spring Boot} to ingest used car data from multiple clients, and store in \imp{MongoDB} cluster.
    \item Built a \imp{React} frontend, enabling users to efficiently filter and search the dataset.
    \item Engineered a dynamic, auto-scaling thread pool for the ingestion pipeline, optimizing resource utilization and throughput based on data volume and API response times.
 \end{itemize}
 
% \eventsubheader{\href{https://forum.xda-developers.com/m/rharshit.4745111/}{XDA Developers}}{Android Systems Development }
\eventsubheader{AOSP Development}{\eventdateplace{May 2013 - Feb 2015}{}}
An independent exploration of Android internals through building custom ROMs, modifying system components, and open-source contributions.
\begin{itemize}
  % \item Developed Android operating system based on \imp{Android Open Source Project (AOSP)}.
  % \item Contributed to \imp{Open Source} projects like \imp{CyanogenMod} and \imp{LineageOS}.
  \item Contributed to \imp{AOSP} derived Open Source projects like \imp{CyanogenMod} and \imp{\href{https://lineageos.org/}{LineageOS}}.
  \item Developed custom Android ROMs focused on enhancing user experience by adding features to framework's \imp{SystemUI}. \superscript{\href{https://xdaforums.com/t/rom-4-4-4-version-1-android-l-themed-omega-rom-screenshots-updated.2687063/}{\linksymbol} \href{https://xdaforums.com/t/rom-4-4-4-beta-1-acerom-halo-hover-headsup-peek.2890223/}{\linksymbol}}
  \item Designed a script to leverage vendor partition to tackle storage limitation on legacy devices.
  \item Shrank the system image footprint by building a resource optimization pipeline that utilized drawable compression and asset removal.
  \item Co-developed device tree for \href{https://github.com/LineageOS/android_device_google_sprout}{Android One}.
  \item Actively maintained a portfolio of AOSP based projects on \href{https://forum.xda-developers.com/m/rharshit.4745111/}{\imp{XDA Developers}}. \superscript{\href{https://xdaforums.com/t/rom-4-4-4-paranoid-android-final-4-4.2789356/}{\linksymbol} \href{https://xdaforums.com/t/rom-4-4-4-version-1-android-l-themed-omega-rom-screenshots-updated.2687063/}{\linksymbol} \href{https://xdaforums.com/t/update-3-rom-4-2-kitkat-for-optimus-one.2514625/}{\linksymbol} \href{https://xdaforums.com/t/rom-5-0-cyanogenmod-12-based-omega-rom-test-1-unofficial.2958665/}{\linksymbol} \href{https://xdaforums.com/t/rom-4-4-4-beta-1-acerom-halo-hover-headsup-peek.2890223/}{\linksymbol}}
 \end{itemize}

 
% \cvsection{Other Projects}
% \eventsubheader{\href{https://github.com/rharshit/WindDown}{Wind Down}}{\eventdateplace{Jan 2019 - Apr 2019}{}}
% \begin{itemize}
%     \item Developed an \imp{Android} application that replicated core phone functionalities, demonstrating deep knowledge of \imp{Android OS} and \imp{SDK}.
%  \end{itemize}
%  \eventsubheader{\href{https://github.com/rharshit/FitnessTracker}{Fitness Tracker}}{\eventdateplace{Oct 2018 - Nov 2018}{}}
%  \begin{itemize}
%     \item \imp{JavaFX} and \imp{MySQL} project to track calories.
% \end{itemize}
% \eventsubheader{HandGest Drone}{\eventdateplace{Feb 2017}{}}
% \begin{itemize}
%    \item Created \imp{OpenCV} app to track and send hand gestures to control drone.
% \end{itemize}

\cvsection{Achievements}
\eventsubheader{\href{https://icpc.global/ICPCID/4BX0YAOPE9W1}{ICPC Regionals}}{}
%\eventdateplace{2018-2019}{}
\begin{itemize}
    \item \imp{Rank 36} in ICPC Kharagpur region, 2018
    \item \imp{Rank 46} in ICPC Kolkata-Kanpur region, 2018
 \end{itemize}
% \eventsubheader{Academic awards}{}
% \begin{itemize}
%    \item Top 1 percentile in high school.
%    \item Awarded silver medal in state-level maths competition.
% \end{itemize}